Test functions on Alabama data

### 2016-09-28 Code/1_Explore_Data_v2.Rmd
more updates

@@

```{r aggregate_over_COD}
dat2 <- dat.clean %>% group_by(State2, Year2, RaceSex, Age2) %>%
  arrange(State2, RaceSex, Year2, Age2) %>%
  summarise(total_deaths1 = sum(Count_md1), 
            total_deaths5 = sum(Count_md5),
            total_deaths9 = sum(Count_md9), 
            total_deaths_b9 = sum(Count_b9w1), 
            total_deaths_w9 = sum(Count_b1w9),
            Population = first(Population), 
            Race2 = first(Race2), 
            Sex2 = first(Sex2), 
            StateYearRaceSex = first(StateYearRaceSex),
            nx = first(nx),
            Age3 = first(Age3),
            Year3 = first(Year3))

>>>>

```{r addvar_cod_proportions}
dat.clean <- dat.clean %>% group_by(State2, RaceSex, Year3, Age3) %>%
                           arrange(State2, RaceSex, Year3, Age3) %>%
                           mutate(total_deaths1 = sum(Count_md1),
                                  total_deaths5 = sum(Count_md5),
                                  total_deaths9 = sum(Count_md9),
                                  cod_prop_death1 = Count_md1/total_deaths1, 
                                  cod_prop_death5 = Count_md5/total_deaths5,
                                  cod_prop_death9 = Count_md9/total_deaths9)
```

@@

```{r aggregate_over_COD}
dat2 <- dat.clean %>% group_by(State2, Year2, RaceSex, Age2) %>%
  arrange(State2, RaceSex, Year2, Age2) %>%
  summarise(Population = first(Population), 
            Race2 = first(Race2), 
            Sex2 = first(Sex2), 
            StateYearRaceSex = first(StateYearRaceSex),
            nx = first(nx),
            Age3 = first(Age3),
            Year3 = first(Year3),
            total_deaths1 = first(total_deaths1),
            total_deaths5 = first(total_deaths5),
            total_deaths9 = first(total_deaths9),
            cod_prop_death1 = first(cod_prop_death1),
            cod_prop_death5 = first(cod_prop_death5),
            cod_prop_death9 = first(cod_prop_death9))

### 2016-09-28 Code/Test life expectancy fxs on Alabama.Rmd
more updates

@@

```{r alabama_example}
library(dplyr)
library(ggplot2)
library(plotly)
load("/Users/corinneriddell/Documents/repos/BlackWhiteGap/Data/alabama_only.Rdata")
#example data

dat.clean.alabama <- dat.clean.alabama %>% mutate(Age3 = 0*(Age2 == "<1 year") + 1*(Age2 == "1-4 years") + 5*(Age2 == "5-9 years") +
                10*(Age2 == "10-14 years") + 15*(Age2 == "15-19 years") + 20*(Age2 == "20-24 years") + 
                25*(Age2 == "25-29 years") + 30*(Age2 == "30-34 years") + 35*(Age2 == "35-39 years") +
                40*(Age2 == "40-44 years") + 45*(Age2 == "45-49 years") + 50*(Age2 == "50-54 years") + 
                55*(Age2 == "55-59 years") + 60*(Age2 == "60-64 years") + 65*(Age2 == "65-69 years") +   
                70*(Age2 == "70-74 years") + 75*(Age2 == "75-79 years") + 80*(Age2 == "80-84 years") + 
                85*(Age2 == "85+ years"))

alabama.by.strata <- 
  dat.clean.alabama %>% group_by(Year2, RaceSex, Age2) %>%
  arrange(RaceSex, Year2, Age2) %>%
  mutate(nx = 1*(Age2 == "<1 year") + 4*(Age2 == "1-4 years") + 5*(Age2 != "<1 year" & Age2 != "1-4 years"))  %>%
  summarise(total_deaths5 = sum(Count_md5),
            Population = first(Population), 
            Race2 = first(Race2), 
            Sex2 = first(Sex2), 
            Year = first(Year),
            Age = first(Age), Age3 = first(Age3),
            StateYearRaceSex = first(StateYearRaceSex),
            nx = first(nx)) %>%
  mutate(mortality_rate = total_deaths5/Population)

>>>>

```{r initialize}
library(dplyr)
library(ggplot2)
library(plotly)
load("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/alabama_only.Rdata")
#example data
```

@@

```{r alabama_example}
alabama.by.strata <- 
  dat.clean.alabama %>% group_by(Year2, RaceSex, Age2) %>%
  arrange(RaceSex, Year2, Age2) %>%
  summarise(total_deaths5 = sum(Count_md5),
            Population = first(Population), 
            Race2 = first(Race2), 
            Sex2 = first(Sex2), 
            Year = first(Year),
            Age = first(Age), Age3 = first(Age3),
            StateYearRaceSex = first(StateYearRaceSex),
            nx = first(nx)) %>%
  mutate(mortality_rate = total_deaths5/Population)
